New approaches for boosting to uniformity

### 2014-10-01 assets/paperdraft/parts/approaches.tex

\subsection{Mean Ada Boost}

@@

After a new tree was built, it's output is altered: for each leaf we can compute such a value, that the result will give the smallest possible value for loss.

...computation of optimal value goes here...

@@

And the post-correction can be handled by using second-order Newton-Raphson optimization step

... TODO computation of optimal value goes here ...

>>>>

\section{Boosting approaches}
\subsection{Mean Ada Boost}

@@

@@

### 2014-10-01 assets/paperdraft/parts/introduction.tex

Methods of machine learning are playing a important role in particles physics nowadays, in particular, multivariate analysis (MVA). 
Different classifiers like boosted decision trees (BDTs) and artificial neural networks (ANNs) are often used as an important step in analysis selection criteria.

@@

The features, along which we want the prediction to be flat, will be referred to as 
\textit{uniform variables}. In high energy physics these are usually masses.

>>>>

Methods of machine learning are playing an important role in particles physics nowadays, in particular, multivariate analysis (MVA). 
Different classifiers like boosted decision trees (BDTs) and artificial neural networks (ANNs) are often used as an important step in analysis selection criteria.

@@

The features, along which we want the prediction to be flat, will be referred to as 
``uniform variables''. In high energy physics these are usually masses.
